Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-05-22 paper/manuscript.Rmd
Double spacing of legends at the end of paper
Remove comment, was showing up in the manuscript
Fix legend of fig. 2 to use ecological factors instead of strategies

\linenumbers
\doublespacing

@@

```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of strategies to minimise competition in the pollination service. (a) The plant's visit effectiveness and relative floral abundance are the most important factors determining the deposition of conspecific and heterospecific pollen. Meanwhile, the number of shared pollinators was generally less important. The graph shows the relative importance calculated as the sum of the Akaike weights of the candidate models that included the selected factor. (b) The association between ecological factors and heterospecific pollen tended to align with their association with conspecific pollen. Visit effectiveness and functional originality had a positive association with pollen deposition, while floral abundance and the number of shared pollinators had a negative association. The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological factors for conspecific and heterospecific pollen. (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and purity of conspecific pollen deposition (relative to heterospecific pollen). The plot shows the model averaged mean effect ($\\pm$ SE of 99 bootstrap replicates)."}
height1 <- 1
height2 <- 1.28
# pdf(width = 3.57 , height = sum(c(height1, height2))*2)
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
# width_imps <- 6.5/5*2
# mult <- 2.455 # for 2/3 is xx, for 3/5 is 2.355
# width_coef_1 <- (6.5 - width_imp) / (1 + mult)
# width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
drake::loadd(fig_coefficient_averages)

>>>>

\linenumbers
\doublespacing
\AtBeginDelayedFloats{%
      \renewcommand{\baselinestretch}{2}}

@@

```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of ecological factors on the pollination service. (a) The plant's visit effectiveness and relative floral abundance are the most important factors determining the deposition of conspecific and heterospecific pollen. Meanwhile, the number of shared pollinators was generally less important. The graph shows the relative importance calculated as the sum of the Akaike weights of the candidate models that included the selected factor. (b) The association between ecological factors and heterospecific pollen tended to align with their association with conspecific pollen. Visit effectiveness and functional originality had a positive association with pollen deposition, while floral abundance and the number of shared pollinators had a negative association. The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological factors for conspecific and heterospecific pollen. (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and purity of conspecific pollen deposition (relative to heterospecific pollen). The plot shows the model averaged mean effect ($\\pm$ SE of 99 bootstrap replicates)."}
height1 <- 1
height2 <- 1.28
# pdf(width = 3.57 , height = sum(c(height1, height2))*2)
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
# width_imps <- 6.5/5*2
# mult <- 2.455 # for 2/3 is xx, for 3/5 is 2.355
# width_coef_1 <- (6.5 - width_imp) / (1 + mult)
# width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
drake::loadd(fig_coefficient_averages)
